\begin{abstract}
	%
	Reservoir models are essential tools for managing oil and gas projects since they can predict the outcomes of different development strategies, thus optimizing the process of decision-making.
	%
	A key source of data for those models is well testing, which provides valuable information about the well and reservoir in a dynamic state.
	%
	The standard workflow of well test interpretation includes calibrating analytical and numerical simulations to observed results, then obtaining well and reservoir data by inverse modeling.
	%
	Creating those numerical models usually requires the upscaling of a high-resolution geological grid into a low-resolution representative model, which is necessary for optimizing the usage of computational power.
	%
	Under certain circumstances, upscaling can generate an accurate representation of those fine-scale models; however, as \cite{Christie1996} states, the accuracy of this process is hardly guaranteed.
	%
	Thus, the main objective of this project is to investigate the effects of upscaling when utilizing numerical simulations to support well test interpretation.
	
	The methodology of this project consists of the development and utilization of a  reservoir simulator.
	%
	This simulator has been developed in C language, resembling a single-phase flow of compressible fluid in the surroundings of a vertical, multilayered well.
	%
	The mathematical model has been discretized by a finite differences approach with a fully implicit temporal discretization.
	%
	Its linearization has been done with what \cite{Ertekin2001} describes as the simple iteration of the transmissibility terms, and the sparse system of equations has been solved by utilizing the UMFPACK (Unsymmetric Multifrontal sparse LU Factorization Package) library.
	%
	This simulator has been validated by comparing its results with simulation done with industry-standard software.
	%
	After this validation, four fine-grid synthetic sandstone models have been created and upscaled into four coarse-grid models.
	%
	Next, those eight cases have been put under a flow simulation for a drawdown test scenario.
	%
	Finally, the results of their bottom-hole pressure, pressure drop, and Bourdet derivative have been analyzed.
	\\
	\\
	\noindent
	\nomenclature[A]{BTCS}{Backwards-time, central-space}
	\nomenclature[A]{UMFPACK}{Unsymmetric Multifrontal sparse LU Factorization Package}
	Keywords: reservoir simulation, well testing, upscaling, single-phase flow.
\end{abstract}