\newpage
\pdfbookmark{Acknowledgments}{acknowledgments} % Sets a PDF bookmark for the dedication
\thispagestyle{empty}

\chapter*{Acknowledgments}
\thispagestyle{empty}

%~Wagner
I cannot express enough thanks to Mr. Wagner Barros, who mentored and guided me since the beginning of this project with unparalleled attention and enthusiasm.
%
His guidance helped me during all the time of research and writing of this project.
%
Without his help, the goal of this work would not have been realized.

%UFES/Joel/AnaPaula
I want to express my sincere gratitude for my professors at the Universidade Federal do Esp\'irito Santo and their contributions to my education.
%
In particular, I want to thank Dr. Oldrich Romero, an enthusiastic professor who guided me in this project and keeps supporting me in several endeavors.
%
I also want to acknowledge the guidance that Dr. Ana Paula Meneguelo provided me in several reservoir engineering aspects relevant to this project.

%CsF/MontanaTech/UT
I thanks CAPES immensely for granting me a sandwich-graduation scholarship with the Science Without Borders Program.
%
This life-changing opportunity allowed me to study abroad in the USA for two semesters at the Montana Technological University and to realize a summer internship at the Bureau of Economic Geology of the University of Texas at Austin.
%
My professors at Montana Tech also have a significant share of contribution to my development as a petroleum engineer, and I thank them very much for this.
%
I want to express my sincere appreciation to Dr. Ian Duncan, who supervised me at the Bureau of Academic Geology with much attention and support. Our conversations at the UT were an enriching source of knowledge in reservoir engineering, geosciences, and a threshold in my academic development.

%Amigos/Gunter
I appreciate the support of my friends, and in particular, of G\"unter Gaede, who shared many hours of his time helping me to troubleshoot and debug the simulator developed in this pŕoject.
%
His assistance was significantly helpful during the first stages of this project.

%Mãe
Finally, I want to express my love and gratitude to my mother, Ruth Soares, for always providing me with unfailing support and care during all my life. Thank you.